Finite-time Analysis of Frequentist Strategies for Multi-armed Bandits

### 2018-01-08 Chapter1/connBandits.tex
Latest on 8/1/2017

As defined in the previous section, an episode consist of a series of sequential interaction where as agent transitions from one state to another based on some intrinsic dynamics of the environment while collecting the rewards and choosing actions based on some action-selecting strategy. Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model. Infact the MAB model can be considered as a single looping state when the agent after taking an action, and observing the reward transitions back to the same state. That single looping state consist of several finite number of actions which are called as arms.

>>>>

As defined in the previous section, an episode consists of a series of sequential interaction whereas agent transitions from one state to another based on some intrinsic dynamics of the environment while collecting the rewards and choosing actions based on some action-selecting strategy. Now, for a single-step interaction, i.e., when the episode terminates after a single transition, the problem is captured by the multi-armed bandit (MAB) model. In fact, the MAB model can be considered as a single looping state when the agent after taking an action and observing the reward transitions back to the same state. That single looping state consists of several finite number of actions which are called as arms.

### 2018-01-08 Chapter1/contribution.tex
Latest on 8/1/2017

\item We proposed the Augmented-UCB (AugUCB) algorithm for a fixed-budget version of the thresholding bandit problem (TBP), where the objective is to identify a set of arms whose quality is above a threshold. A key feature of AugUCB is that it uses both mean and variance estimates to eliminate arms that have been sufficiently explored. This is the first algorithm to employ such an approach for the considered TBP. Furthermore, in numerical evaluations we establish in several considered environments that AugUCB outperforms all the algorithms that does not take into consideration the variance of the arms in their action selection strategy.

\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in context of the piecewise stochastic  distributions. The algorithms that we proposed for the piecewise stochastic setting are actively adaptive algorithms which performs very similarly to the oracle algorithm which has access to the changepoints and suffers no additional delay in adapting to the changing environment. 
\end{enumerate}

>>>>

\item We proposed the Augmented-UCB (AugUCB) algorithm for a fixed-budget version of the thresholding bandit problem (TBP), where the objective is to identify a set of arms whose quality is above a threshold. A key feature of AugUCB is that it uses both mean and variance estimates to eliminate arms that have been sufficiently explored. This is the first algorithm to employ such an approach for the considered TBP. Furthermore, in numerical evaluations, we establish in several considered environments that AugUCB outperforms all the algorithms that do not take into consideration the variance of the arms in their action selection strategy.

%\item We proposed a general framework of bandit algorithms that combines change-point detection algorithm with aggregation of expert strategies in order to define efficient pulling strategies in the context of the piecewise stochastic distributions. The algorithms that we proposed for the piecewise stochastic setting are actively adaptive algorithms which perform very similarly to the oracle algorithm which has access to the changepoints and suffers no additional delay in adapting to the changing environment. 
\end{enumerate}

### 2018-01-08 Chapter1/feedback.tex
Latest on 26/11/2017
Latest on 8/1/2017

	To illustrate the different types of feedback we will take help of the following example. Let a learner be given a set of finite actions $i\in\A$ such that $|\A|=K$. Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$. The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $R^{obs}_{t}$ (which will be characterized later). Before the learner selects the  the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback. This game is shown in algorithm \ref{alg:OSeqGame}.

\begin{algorithm}[!th]
\caption{An online sequential game}
\label{alg:OSeqGame}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
\State The learner chooses $m$ actions such that $m < K$, where $\A$ is the set of arms and $|\A|=K$.
\State The learner observes the reward vector $R^{obs}_{t}\subseteq F^{env}_{t}$.
\State \EndFor
\end{algorithmic}
\end{algorithm}

%Let $G(V,E)$ denote a graph where $V$ denotes the set of nodes in the graph and $E$ denotes the set of edges of the graph. Let there be a single starting node, denoted by $\mathcal{s}\in V$ from where the learner must start and try to reach the destination node denoted by $\mathcal{d}\in V$. Each edge has a delay associated with it which is unknown to the learner. This delay is an $i.i.d$ random variable from the distribution $D_{ij}$ associated with the edge $e_{ij}$ between the vertices $v_i$ and $v_j$. Whenever an edge is chosen the environment reveals to the learner  At every timestep the learner chooses a set of edges and receives some form of feedback from the environment. The goal of the learner is to find the path from $s$ to $d$ which has the minimum delay associated with it.

>>>>

    To illustrate the different types of feedback we will take help of the following example. Let a learner be given a set of finite actions $i\in\A$ such that $|\A|=K$. Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$. The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $R^{obs}_{t}$ (which will be characterized later). Before the learner selects the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback. This game is shown in algorithm \ref{alg:OSeqGame}.

\begin{algorithm}[!th]
\caption{An online sequential game}
\label{alg:OSeqGame}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
\State The learner chooses $m$ actions such that $m < K$ following some policy $\pi$, where $\A$ is the set of arms and $|\A|=K$.
\State The learner observes the reward vector $R^{obs}_{t}\subseteq F^{env}_{t}$.
\State \EndFor
\end{algorithmic}
\end{algorithm}

%Let $G(V, E)$ denote a graph where $V$ denotes the set of nodes in the graph and $E$ denotes the set of edges of the graph. Let there be a single starting node, denoted by $\mathcal{s}\in V$ from where the learner must start and try to reach the destination node denoted by $\mathcal{d}\in V$. Each edge has a delay associated with it which is unknown to the learner. This delay is an $i.i.d$ random variable from the distribution $D_{ij}$ associated with the edge $e_{ij}$ between the vertices $v_i$ and $v_j$. Whenever an edge is chosen the environment reveals to the learner  At every timestep the learner chooses a set of edges and receives some form of feedback from the environment. The goal of the learner is to find the path from $s$ to $d$ which has the minimum delay associated with it.

### 2018-01-08 Chapter1/motivation.tex
Latest on 8/1/2017

\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \citep{thompson1933likelihood},\citep{thompson1935theory}. Here at every timestep, the learner chooses to administer one out of several treatments sequentially on a stream of patients who are suffering from the same ailment (say). Let's also assume that there is a single treatment which will be able to alleviate the patients from their disease. Here, the  one-step interaction ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient. The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relive the patient of its ailment with a high probability. This problem can also be modeled as a stochastic MAB problem.
\item \emph{Financial Portfolio Management:} In financial portfolio management MAB models can also be used. Here, the learner is faced with the choice of selecting the most profitable stock option out of several stock options. The simplest strategy where we can employ a bandit model is this; at the start of every trading session the learner suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading. The  profit recorded is treated as the reward revealed by the environment and the learner modifies its policy for the next day. Let's assume that no new stock options are being introduced over the considered time horizon and there is a single best stock option which if selected for perpetuity will always give the best returns. Then, the goal of the learner is reduced to identifying the best stock option as quickly as possible. This is another interesting variation which can modeled as a stochastic MAB problem.
\item \emph{Product Selection:} A company wants to introduce a new product in market and there is a clear separation of the test phase from the commercialization phase. In this case the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase. So from the several variants of the product that are in the test phase the learning learner must suggest the product variant(s) whose qualities are above a particular threshold $\tau$ at the end of the test phase that have the highest probability of minimizing loss in the commercialization phase. A similar problem has been discussed for single best product variant identification without threshold in \citet{bubeck2011pure}. This problem can be modeled as a stochastic thresholding MAB problem which is studied in the second part of the thesis.
\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications \citep{audibert2009exploration}. Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learner has to explore as many channels as possible to suggest the best possible set of channel(s) whose qualities are above a particular threshold $\tau$. The threshold may depend on the subscription level of the customer such that with higher subscription the customer is allowed better channel(s) with the $\tau$ set high. Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible set of suggestions within a very small  number of attempts. This setting can also be modeled as a stochastic thresholding MAB problem.

>>>>

\item \emph{Medical Treatment Design:} Another interesting domain that MAB model was first studied was for the medical treatment design \citep{thompson1933likelihood},\citep{thompson1935theory}. Here at every timestep, the learner chooses to administer one out of several treatments sequentially on a stream of patients who are suffering from the same ailment (say). Let's also assume that there is a single treatment which will be able to alleviate the patients from their disease. Here, the one-step interaction ends when the patient responds well or does not respond well to the treatment whereby the learner modifies its policy for the suggestion to the next patient. The goal of the learner is to quickly converge on the best treatment so that whenever a new patient comes with the same ailment, the learner can suggest the best treatment which can relieve the patient of its ailment with a high probability. This problem can also be modeled as a stochastic MAB problem.
\item \emph{Financial Portfolio Management:} In financial portfolio management MAB models can also be used. Here, the learner is faced with the choice of selecting the most profitable stock option out of several stock options. The simplest strategy where we can employ a bandit model is this; at the start of every trading session, the learner suggests a stock to purchase worth Re $1$, while at the closing of the trading session it sells off the stock to witness its value after a day's trading. The profit recorded is treated as the reward revealed by the environment and the learner modifies its policy for the next day. Let's assume that no new stock options are being introduced over the considered time horizon and there is a single best stock option which if selected in perpetuity will always give the best returns. Then, the goal of the learner is reduced to identifying the best stock option as quickly as possible. This is another interesting variation which can be modeled as a stochastic MAB problem.
\item \emph{Product Selection:} A company wants to introduce a new product in the market and there is a clear separation of the test phase from the commercialization phase. In this case, the company tries to minimize the loss it might incur in the commercialization phase by testing as much as possible in the test phase. So from the several variants of the product that is in the test phase, the learning learner must suggest the product variant(s) whose qualities are above a particular threshold $\tau$ at the end of the test phase that has the highest probability of minimizing the loss in the commercialization phase. A similar problem has been discussed for single best product variant identification without threshold in \citet{bubeck2011pure}. This problem can be modeled as a stochastic thresholding MAB problem which is studied in the second part of the thesis.
\item \emph{Mobile Phone Channel Allocation:} Another similar problem as above concerns channel allocation for mobile phone communications \citep{audibert2009exploration}. Here there is a clear separation between the allocation phase and communication phase whereby in the allocation phase a learner has to explore as many channels as possible to suggest the best possible set of channel(s) whose qualities are above a particular threshold $\tau$. The threshold may depend on the subscription level of the customer such that with the higher subscription the customer is allowed better channel(s) with the $\tau$ set high. Each evaluation of a channel is noisy and the learning algorithm must come up with the best possible set of suggestions within a very small number of attempts. This setting can also be modeled as a stochastic thresholding MAB problem.

### 2018-01-08 Chapter1/objective.tex
Latest on 8/1/2017

The main objectives of the thesis are as follows:-
\begin{enumerate}
\item The first objective of this thesis is to study the area of stochastic multi-armed bandit (SMAB) and how to minimize cumulative regret in this setup. We intend to give strong gap-dependent and gap-independent regret guarantees in the SMAB setting. We also intend to provide algorithm in the SMAB setting that outperforms the current state-of-the-art algorithms in this setting.

\item The second objective of this thesis is to study the area of thresholding bandit problem (TBP) setting where the goal is to minimize the expected loss at the end of a fixed budget provided as input. We intend to provide strong guarantees with respect to expected loss and also propose algorithm that does not require any problem complexity as an input. We also intend to provide strong empirical evaluations of the algorithm proposed for the TBP setting.

\item The third objective of this thesis is to study the area of piecewise stochastic bandit where again the goal is to minimize the cumulative regret. We intend to provide strong algorithms that can adapt to this environment and performs well empirically.  
\end{enumerate}

>>>>

The main objectives of the thesis are as follows:-
\begin{enumerate}
\item The first objective of this thesis is to study the area of stochastic multi-armed bandit (SMAB) and how to minimize cumulative regret in this setup. We intend to give strong gap-dependent and gap-independent regret guarantees in the SMAB setting. We also intend to provide the algorithm in the SMAB setting that outperforms the current state-of-the-art algorithms in this setting.

\item The second objective of this thesis is to study the area of thresholding bandit problem (TBP) setting where the goal is to minimize the expected loss at the end of a fixed budget provided as input. We intend to provide strong guarantees with respect to expected loss and also propose the algorithm that does not require any problem complexity as an input. We also intend to provide strong empirical evaluations of the algorithm proposed for the TBP setting.

%\item The third objective of this thesis is to study the area of piecewise stochastic bandit where again the goal is to minimize the cumulative regret. We intend to provide strong algorithms that can adapt to this environment and performs well empirically.  
\end{enumerate}

### 2018-01-08 Chapter1/studyBandit.tex
Latest on 8/1/2017

There are multiple reasons to study the interesting area of bandits. First of all, bandits are the cornerstone of understanding the general reinforcement learning area. Infact, bandits helps us to understand the idea of \textit{exploration-exploitation} dilemma which is the basis to build full, multi-state, general reinforcement learning ideas. Secondly, as stated in \citet{maillard2011apprentissage}, even $50$ years after \cite{robbins1952some} introduced the first idea of bandits, there are many interesting and fruitful areas where bandit concept can be extended in both practical and theoretical terms. Finally, there are several real-life industrial applications ranging from recommendation systems, game theory to anomaly detection where bandit applications have been found to perform exceptionally well. All of these forces us to delve deep into a systemic research of bandits.

>>>>

There are multiple reasons to study the interesting area of bandits. First of all, bandits are the cornerstone of understanding the general reinforcement learning area. In fact, bandits help us to understand the idea of \textit{exploration-exploitation} dilemma which is the basis to build full, multi-state, general reinforcement learning ideas. Secondly, as stated in \citet{maillard2011apprentissage}, even $50$ years after \cite{robbins1952some} introduced the first idea of bandits, there are many interesting and fruitful areas where bandit concept can be extended in both practical and theoretical terms. Finally, there are several real-life industrial applications ranging from recommendation systems, game theory to anomaly detection where bandit applications have been found to perform exceptionally well. All of these forces us to delve deep into a systemic research of bandits.

### 2018-01-08 Chapter2/motivation.tex
Latest on 8/1/2017

There has been a significant amount of research in the area of stochastic MABs. One of the earliest work can be traced to \citet{thompson1933likelihood}, which deals with  the problem of choosing between two treatments to administer on patients who come in sequentially. In \citet{thompson1935theory} this work was extended to include more general cases of finitely many treatments. In recent years the SMAB setting has garnered extensive popularity because of its simple learning  model and its practical applications in a wide-range of industries, including, but not limited to, mobile channel allocations, online advertising and computer simulation games. Some of these problems have been already discussed in chapter \ref{chap:intro}, section \ref{motivation} and an interested reader can refer to it.

>>>>

There has been a significant amount of research in the area of stochastic MABs. One of the earliest work can be traced to \citet{thompson1933likelihood}, which deals with the problem of choosing between two treatments to administer to patients who come in sequentially. In \citet{thompson1935theory} this work was extended to include more general cases of finitely many treatments. In recent years the SMAB setting has garnered extensive popularity because of its simple learning model and its practical applications in a wide-range of industries, including, but not limited to, mobile channel allocations, online advertising and computer simulation games. Some of these problems have been already discussed in chapter \ref{chap:intro}, section \ref{motivation} and an interested reader can refer to it.

### 2018-01-08 Chapter4/intro.tex
Latest on 8/1/2017

In the previous chapters \ref{chap:SMAB} and \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret. In this chapter we will study another setting called Pure-exploration multi-armed bandits. An interested reader can read through the previous chapters or can continue from here. Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup are mentioned in this chapter itself. Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the  objective is to minimize the cumulative regret. The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. 
	In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.  In this chapter, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).  Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to  output all arms $i$ whose $r_{i}$ is above $\tau$. 
It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives an unit reward whenever the value of an observation is above a threshold.

>>>>

In the previous chapters \ref{chap:SMAB} and \ref{chap:EUCBV} we studied the stochastic multi-armed bandit (SMAB) setting with the goal of minimizing cumulative regret. In this chapter, we will study another setting called Pure-exploration multi-armed bandits. An interested reader can read through the previous chapters or can continue from here. Though we re-use the ideas from SMABs, the goal of pure exploration setup is distinctly different from that of cumulative regret minimization of SMABs and the required algorithms to understand this setup are mentioned in this chapter itself. Pure-exploration MAB problems are unlike their traditional (exploration vs.\ exploitation)  counterparts, the SMABs, where the objective is to minimize the cumulative regret. The cumulative regret is the total loss incurred by the learner for not playing the optimal arm throughout the time horizon $T$. 
    In pure-exploration problems a learning algorithm, until time $T$, can invest entirely on exploring the arms without being concerned about the loss incurred while exploring; the objective is to minimize the probability that the arm recommended at time $T$ is not the best arm.  In this chapter, we further consider a combinatorial version of the pure-exploration MAB, called the thresholding bandit problem (TBP).  Here, the learning algorithm is provided with a threshold $\tau$, and the objective, after exploring for $T$ rounds, is to output all arms $i$ whose $r_{i}$ is above $\tau$. 
It is important to emphasize that the \emph{thresholding} bandit problem is different from the \emph{threshold} bandit setup studied in \cite{abernethy2016threshold}, where the learner receives a unit reward whenever the value of an observation is above a threshold.

### 2018-01-08 Chapter4/prevRes.tex
Latest on 8/1/2017

Significant amount of literature is available on the stochastic MAB setting with respect to minimizing the cumulative regret. Chapter \ref{chap:SMAB} and \ref{chap:EUCBV} deals with that. In this work we are particularly interested in \emph{pure-exploration MABs},  where the focus in primarily on simple regret rather than the cumulative regret. The relationship between cumulative regret and simple regret is proved in \citet{bubeck2011pure} where the authors prove that minimizing the simple regret necessarily results in maximizing the cumulative regret.
The pure exploration problem has been explored  mainly under the following two settings:

@@

The goal in best p-arms setting is to identify the top $p$ arms out of $K$ given arms where $p$ is supplied as an input. Several algorithms have been proposed for these setup starting with \citet{gabillon2011multi} where the authors proposed the GapE and GapE-V algorithms that suggest, with high probability, the best-$p$ arms at the end of the time budget. These algorithms are similar to the UCBE type algorithm discussed in previous section. In this section we will discuss the Successive Accept Reject strategy shown in algorithm \ref{alg:sar}.

@@

In this setting the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible. The single best arm identification has been studied in \citet{even2006action}, while for the combinatorial setup \citet{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$. For a detail survey of this setup we refer the reader to \citet{jamieson2014best}.

>>>>

A significant amount of literature is available on the stochastic MAB setting with respect to minimizing the cumulative regret. Chapter \ref{chap:SMAB} and \ref{chap:EUCBV} deals with that. In this work, we are particularly interested in \emph{pure-exploration MABs},  where the focus is primarily on simple regret rather than the cumulative regret. The relationship between cumulative regret and simple regret is proved in \citet{bubeck2011pure} where the authors prove that minimizing the simple regret necessarily results in maximizing the cumulative regret.
The pure exploration problem has been explored  mainly in the following two settings:

@@

The goal in the best p-arms setting is to identify the top $p$ arms out of $K$ given arms where $p$ is supplied as an input. Several algorithms have been proposed for this setup starting with \citet{gabillon2011multi} where the authors proposed the GapE and GapE-V algorithms that suggest, with high probability, the best-$p$ arms at the end of the time budget. These algorithms are similar to the UCBE type algorithm discussed in the previous section. In this section, we will discuss the Successive Accept Reject strategy shown in algorithm \ref{alg:sar}.

@@

In this setting, the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible. The single best arm identification has been studied in \citet{even2006action}, while for the combinatorial setup \citet{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$. For a detailed survey of this setup, we refer the reader to \citet{jamieson2014best}.

### 2018-01-08 Chapter4/prevResAPT.tex
Latest on 8/1/2017

In the latest work of \citet{locatelli2016optimal} Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem. APT is stated in algorithm \ref{alg:apt}.

@@

The APT algorithm is very simple to implement and the logic behind the arm pull directly follows from the challenges in the TBP setting discussed before. Note, that the most difficult arms to discriminate are the arms whose expected means are lying close to the threshold $\tau$, hence APT pulls those arms whose sample means $\hat{r}_i$ are lying close to the threshold and the arms which has not been pulled often. The second condition is satisfied by the $\sqrt{n_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see algorithm \ref{alg:ucbe}). The tolerance level $\epsilon\geq 0$ gives the algorithm a degree of flexibility in pulling the arms close to the threshold.

>>>>

In the latest work of \citet{locatelli2016optimal}, Anytime Parameter-Free Thresholding (APT) algorithm comes up with an improved anytime guarantee than CSAR for the thresholding bandit problem. APT is stated in algorithm \ref{alg:apt}.

@@

The APT algorithm is very simple to implement and the logic behind the arm pull directly follows from the challenges in the TBP setting discussed before. Note, that the most difficult arms to discriminate are the arms whose expected means are lying close to the threshold $\tau$, hence APT pulls those arms whose sample means $\hat{r}_i$ are lying close to the threshold and the arms which have not been pulled often. The second condition is satisfied by the $\sqrt{n_i}$ term which acts very similar to the confidence interval term discussed for UCBE (see algorithm \ref{alg:ucbe}). The tolerance level $\epsilon\geq 0$ gives the algorithm a degree of flexibility in pulling the arms close to the threshold.
